\documentclass[10pt, twocolumn]{recipe}
\title{Egg Tomato Noodles\vspace{-3em}}
\begin{document}
\maketitle
\begin{ingredients}
  \Item 2 Eggs
  \Item 1 Tomato
  \Item 1 green onion leaf
  \Item 1 slice of ginger
  \Item Canola oil
  \Item Noodles
  \Item \Sauce Better Than Bouillon
  \Item \Sauce Viet Huong
\end{ingredients}

\begin{equipment}
  \Item Pan
  \Item Pot
  \Item Knife and cutting board
  \Item Spatula (wood or rubber)
  \Item 1 bowl to stir eggs + fork or chopsticks
  \Item 1 bowl for finished noodles
  \Item \Optional Oil splash-blocker
\end{equipment}

\begin{procedure}
\Step fill pot with $3cm$ of water. Put lid on. Turn fire to max
\Step prepare 1 tomato into chunks. Split half, then half, then half, then into three. Crack 2 eggs into bowl and stir. Prepare 1 green onion. Cut off head. Cut in half (-- --). Cut into disks. Prepare 1 slice of ginger, radius $1cm$
\Step put pan with largest fire. Add oil into pan
\Note add enough oil so it just covers pan, not too much because non-stick, but not a few drops either
\Note wait for the pan to heat up a bit, but don't wait for it to become too hot because non-stick pan
\Step when oil is hot, add in eggs
\Note oil is hot when it is steamy
\Note let egg cook for 5 seconds before scrambling again. Do not continuously scramble
\Step put eggs back into egg bowl when solid
\Step add oil into pan again, slightly less than before
\Step when oil is hot, add green onions + ginger. Wait 3 seconds. Turn fire to low
\Step add in tomato. Scoop tomato with knife side, don't dump entire cuttingboard's worth at once. May use splash-blocker
\Step turn fire to max. Wait 30-60 seconds until sizzling sound. Mix. Repeat until tomatos are fuzzy.
\Step add eggs. Make sure to cut into smaller chunks. Mix for 1 minute, max fire.
\Step add salt ($\frac{1}{4}$ of $1cm^3$) and soy-sauce (small stream half-centimeter in diameter for 2 seconds). Mix.
\Step add water until most of the food is covered. Mix. Add lid. Wait until water boils, then turn fire to small, make sure to keep boil. Keep this going for around 10 minutes.
\Step pot should be boiling. Add noodles.
\Note amount of noodles: OK sign with index nail on first joint of my thumb
\Note to add noodles, put vertically in middle of pot, then make *
\Note make sure noodles don't stick to eachother OR stick to the bottom. Make sure to stir the noodles once every 2 minutes
\Note do not add lid else may overpour
\Note now is the time to double-check on pan and make sure water is boiling
\Step when noodles are $\frac{1}{6}$ translucent on both sides (or $\frac{1}{3}$ of strand) turn fire off
\Step taste soup in pan. Add salt if necessary. Add sauces: one small spoonful of Better Than Bouillon, 1/3 soy-sauce amount of Viet Huong.
\Step move noodles to saucepan. Turn fire off. Mix.
\Note Don't want water on the noodles. Make sure to let them drip first
\Step move noodles into bowl.
\Step immediately wash pot and pan while they are hot. Also wash other equipment used
\Note Dry pot and pan


\end{procedure}




\end{document}
